---
title: "my-vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(rpkgs.playground)
```

Below is an example call to function `rpkgs.playground::mfl()`. 

```{r}
mfl()
```

Below code tries to read a `.csv` file under the same folder. 

```{r}
# Pay attention to path that `read.csv()` uses
tb <- tidyr::as_tibble(read.csv("ext1.csv", stringsAsFactors = FALSE))
tb
```

## Code chunk options

Below is for testing out code chunk options `include` and `echo`. Below is the 
result of the code chunk who have option `include = FALSE`. We don't expect any 
results printed in rendered file. 

```{r, include = FALSE}
message("This message is printed in a code chunk with `include = FALSE`. ")
```

And this is results of code chunk with option `echo = FALSE`. 

```{r, echo = FALSE}
message("This message is printed in a code chunk with `echo = FALSE`. ")
```
